Multi-Task Mutual Learning for Vehicle Re-Identification

### 2019-05-08 paper.tex
Add Jimmy's changes and Aytac's results.

%%%%%%%%% ABSTRACT
\begin{abstract}
Vehicle re-identification (Re-ID) aims to search a specific vehicle
instance across non-overlapping camera views.
%
The main challenge of vehicle Re-ID is that
the visual appearance of vehicles may drastically changes
according to diverse viewpoints and illumination.
%
Most of existing vehicle Re-ID model cannot make full use of
various complementary vehicle information, e.g. vehicle type and orientation.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative features simultaeously from multiple branches.
%
Specially, we design a consensus learning loss function by fusing features from the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of our
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID and VeRi-776).
We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
\end{abstract}

@@

We make two contributions in this work as follows:
(1) We formulate a novel {\em Multi-Task Mutual Learning} (MTML) deep
learning model by building each individual branch for a different
recognition task relevant to vehicle Re-ID and by taking into
consideration four different tasks: vehicle ID, multi-scale, grayscale, and orientation.
Our model aims to discover and capture concurrently the complementary discriminative information.
(2) We introduce a mutual learning mechanism for improving multi-task learning robustness.
Our model benefits from multiple supervisory signals in order to
enhance model learning of more discrimative features for vehicle Re-ID.
%(3) we propose a cross-dataset joint learning framework for vehicle Re-ID.
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID \cite{liu2016vehicleid} and VeRi-776 \cite{liu2016veri}).
We also yield competitive performance on the CityFlow
\cite{tang2019cityflow} benchmark at the NVIDIA 2019 AI City Challenge.

@@

\subsection{Evaluation on the Veri776 Dataset}
Firstly, we train and test on the VeRi776 dataset in order to compare with
existing state-of-the-art methods with identical settings. In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and of course all models have an E consensus branch, and then perform experiments where we include each of the other branches in turn. So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on. We then test versions of the model with three branches (e.g. MTML-SG includes branches A, B, C and E).  MTML-OSG is then our full model, and MTML-OSG (ReRank) the results of the full model after additional re-ranking. Table \ref{T:benchmark_results_veri} shows the results of this
experiment, with all experiments run for 150 epochs of training. As can be seen,
even before re-ranking, our full model achieves state-of-the-art mAP
and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
respectively. And after re-ranking the mAP score is increased to an
impressive 68.3\%.

@@

\subsection{NVIDIA AI City Challenge 2019}

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    Resnet50\cite{tang2019cityflow} & 25.5 & 41.3 & - \\
    \hline
    MTML-S  & 17.0 & 40.4 & 53.3 \\
    MTML-G  & 19.6 & 44.5 & 58.4 \\
    \hdashline
    MTML-SG & 20.6 & 44.1 & 55.8 \\
    \hdashline
    MTML-SG (ReRank) &  & & \\
    \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow}
  \label{T:cityflow_results}
\end{table}

\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{0.05cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \multicolumn{1}{r|}{Test:} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
  \hline
  Method       & mAP   & Rank-1  & Rank-5  & mAP   & Rank-1 & Rank-5  \\
  \hline
  MTML-O       &       &         &         &       &        &         \\
  MTML-S       &       &         &         &       &        &         \\
  MTML-G       & 61.6  & 89.7    & 95.1    &       &        &         \\
  MTML-SG      & 62.6  & 90.8    & 95.8    &       &        &         \\
  MTML-OG      &       &         &         &       &        &         \\
  MTML-OSG     &       &         &         &       &        &      \\
  \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow+VeRi-776}
  \label{T:cf_veri_res}
\end{table}

@@

@@

\section{Conclusions}
Vehicle Re-ID is difficult because the visual appearance of
a vehicle instance may drastically change due to diverse
viewpoints and illumination, whilst different vehicle instances of the same
model type may have a very similar appearance.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Moreover, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the two existing benchmarks
(VehicleID and VeRi-776).
We also yield a competitive performance on the NVIDIA 2019 AI City Challenge Track 2.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Vehicle re-identification (Re-ID) aims to search a specific vehicle
instance across non-overlapping camera views.
%
The main challenge of vehicle Re-ID is that
the visual appearance of vehicles may drastically changes
according to diverse viewpoints and illumination.
%
Most of existing vehicle Re-ID model cannot make full use of
various complementary vehicle information, e.g. vehicle type and orientation.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative features simultaeously from multiple branches.
%
Specially, we design a consensus learning loss function by fusing features from the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of our
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a large-scale benchmarks VeRi-776.
We also yield competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
\end{abstract}

@@

We make two contributions in this work as follows:
(1) We formulate a novel {\em Multi-Task Mutual Learning} (MTML) deep
learning model by building each individual branch for a different
recognition task relevant to vehicle Re-ID and by taking into
consideration four different tasks: vehicle ID, multi-scale, grayscale, and orientation.
Our model aims to discover and capture concurrently the complementary discriminative information.
(2) We introduce a mutual learning mechanism for improving multi-task learning robustness.
Our model benefits from multiple supervisory signals in order to
enhance model learning of more discrimative features for vehicle Re-ID.
%(3) we propose a cross-dataset joint learning framework for vehicle Re-ID.
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a large-scale benchmark
%VehicleID \cite{liu2016vehicleid} and 
VeRi-776 \cite{liu2016veri}.
We also yield competitive performance on the CityFlow
\cite{tang2019cityflow} benchmark at the NVIDIA 2019 AI City Challenge.

@@

\subsection{Evaluation on Veri776 Dataset}
Firstly, we train and test on the VeRi776 dataset in order to compare with
existing state-of-the-art methods with identical settings. In order to experiment the benefit of adding each of the separate branches of our model, we take branch A (vehicle identity) as our central branch, and of course all models have an E consensus branch, and then perform experiments where we include each of the other branches in turn. So MTML-S refers to a model built from branches A, B and E only, MTML-G has branches A, C and E only, and so on. We then test versions of the model with three branches (e.g. MTML-SG includes branches A, B, C and E).  
MTML-OSG (branches A, B, C, D and E) is then our full model, and MTML-OSG (ReRank \cite{zhong2017re}) the results of the full model after additional re-ranking. Table \ref{T:benchmark_results_veri} shows the results of this
experiment, with all experiments run for 150 epochs of training. As can be seen,
even before re-ranking, our full model achieves state-of-the-art mAP
and Rank-1 scores on this dataset, of 64.6\% and 92.3\%
respectively. And after re-ranking the mAP score is increased to an
impressive 68.3\%.

@@

\subsection{Evaluation on CityFlow Dataset}

\begin{table}[h]
  \centering
  \begin{tabular}{l || c | c | c }
    \hline
    Method & mAP & Rank-1 & Rank-5 \\
    \hline
    Resnet50 \cite{tang2019cityflow} & 25.5 & 41.3 & - \\
    \hline
    MTML-S  & 17.0 & 40.4 & 53.3 \\
    MTML-G  & 19.6 & 44.5 & 58.4 \\
    \hdashline
    MTML-SG & 20.6 & 44.1 & 55.8 \\
    \hdashline
    MTML-SG (ReRank) &  & & \\
    \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow}
  \label{T:cityflow_results}
\end{table}

\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{0.05cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \multicolumn{1}{r|}{Test:} & \multicolumn{3}{c|}{VeRi-776} & \multicolumn{3}{c}{CityFlow} \\
  \hline
  Method       & mAP   & Rank-1  & Rank-5  & mAP   & Rank-1 & Rank-5  \\
  \hline
  MTML-O       &       &         &         &       &        &         \\
  MTML-S       &       &         &         &       &        &         \\
  MTML-G       & 61.6  & 89.7    & 95.1    & 22.3  & 47.4   & 57.3   \\
  MTML-SG      & 62.6  & 90.8    & 95.8    & 23.0  & 46.6   & 60.5   \\
  MTML-OG      &       &         &         &       &        &         \\
  MTML-OSG     &       &         &         &       &        &      \\
  \hline
  \end{tabular}
  \caption{Trained/tested on CityFlow+VeRi-776}
  \label{T:cf_veri_res}
\end{table}

@@

Two groups of experiments are conducted on CityFlow benchmark: 
(1) Training on CityFlow, and (2) Training on CityFlow and Veri-776.
%
For the first group experiment, we trained MTML-S (branch A, B and E), 
MTML-G (branch A, C and E) and MTML-SG model only on CityFlow training data.
Table \ref{T:cityflow_results} shows that: 
(1) -G branch combination is much better than -S branch combination. 
The potential reason is that grayscale analysis is more useful than mult-scale in vehicle Re-ID.
(2) Joint learning with -S and -G is better than any individual one of them on mAP evaluation.

%The reason of combine Veri-776 dataset into training set is that
Since the orientation label is only available in Veri-776, 
for training the full MTML model including orientation supervisory signal,
we did the second group experiment.
%
%Table \ref{T:cf_veri_res} shows that:

@@

\section{Conclusions}
Vehicle Re-ID is difficult because the visual appearance of
a vehicle instance may drastically change due to diverse
viewpoints and illumination, whilst different vehicle instances of the same
model type may have a very similar appearance.
%
In this paper, we propose a novel {\em Multi-Task Mutual Learning} (MTML) deep model
to learn discriminative feature simultaeously from multiple branches.
%
Moreover, we design a consensus learning loss function by fusing feature of the final convolutional feature maps from all branches.
%
Extensive comparative evaluations demonstrate the effectiveness of the
proposed MTML method in comparison to the state-of-the-art vehicle Re-ID techniques on the a existing large-scale benchmarks VeRi-776.
%VehicleID and
We also yield a competitive performance on the NVIDIA 2019 AI City Challenge Track 2.
